TCP Congestion Algorithms In Datacenters \\ \vspace{0.3cm} {\large LS Project}

### 2017-12-01 paper/paper.tex
Added sources

	\subsection{Traffic Management}
	Desk research will be conducted to gather information related to traffic management. The goal is to find a mechanism that is capable of allocating equally between customers of a datacenter. This is done by analyzing the results from the algorithm comparison and the initial desk research on traffic management.

\section{Results}
	\subsection{TCP Congestion Algorithms}
	The most common TCP congestion algorithms are CTCP, CUBIC and BIC. CTCP is the default congestion algorithm in Microsoft Windows Server Editions and Microsoft Windows 8 and newer [SRC]. CUBIC is the default congestion algorithm in Linux distributions with kernel versions ... and newer [SRC]. BIC was the default congestion algorithm in earlier Linux distributions with kernel versions: [SRC]. DCTCP and BBR will also be tested as those protocols are newer. DCTCP is specifically designed for datacenters [SRC] and BBR is a new congestion protocol not yet widely deployed [SRC].

@@

\begin{enumerate}
	\item What TCP congestion algorithms are most commonly implemented in datacenter environments?
	\item How do these TCP congestion algorithms work?
	\item How do these TCP congestion algorithms differ in behavior?
	\item What is the impact on the availability and service for customers when using different, competing congestion algorithms?
	\item What measures could be taken to split bandwidth equally among tenants?
\end{enumerate}

>>>>

	\subsection{Traffic Management}
	Desk research will be conducted to gather information related to traffic management. The goal is to find a mechanism that is capable of allocating bandwidth equally between customers of a datacenter. This is done by analyzing the results from the algorithm comparison and the initial desk research on traffic management.

\section{Results}
	\subsection{TCP Congestion Algorithms}
	The most common TCP congestion algorithms are CTCP, CUBIC and BIC. CTCP is the default congestion algorithm in Microsoft Windows Server 2008 and newer \cite{cubic-kernel-version}. CUBIC is the default congestion algorithm in Linux distributions with kernel versions 2.6.19 and higher \cite{cubic-kernel-version}. BIC was the default congestion algorithm in earlier Linux distributions from kernel version 2.6.8 until 2.6.19 \cite{bic-kernel-version} \cite{cubic-kernel-version}. DCTCP and BBR will also be tested as those protocols are newer. DCTCP is specifically designed for datacenters \cite{dctcp-congestion} and BBR is a new congestion protocol not yet widely deployed \cite{bbr-congestion}.

@@

\begin{enumerate}
	\item What TCP congestion algorithms are most commonly implemented?
	\item How do these TCP congestion algorithms work?
	\item How do these TCP congestion algorithms differ in behavior?
	\item What is the impact on the availability and service for customers when using different, competing congestion algorithms?
	\item What measures could be taken to split bandwidth equally among tenants?
\end{enumerate}
